A weakly structured stem for human origins in Africa

### 2023-03-01 paper.tex
updated author contributions
Acknowledgement and access

We are grateful for the DNA contribution from each participant that enabled
this study; in particular we wish to highlight the generous participation of
the Richtersveld Nama community in South Africa and help from local research
assistants Willem DeKlerk and Hendrik Kaimann. Additional assistance and
community engagement was conducted by Justin Myrick, Chris Gignoux, Caitlen
Uren and Cedric Werely. We thank the African Genome Diversity Project for data
generation, including Tommy Carensten, Deepti Gurdasani, and Manj Sandhu. We
thank Luke Anderson-Trocm\'e and Georgette Femerling for assistance in creating
the map in Figure~\ref{fig:diversity} and Figure \ref{fig:toymodels},
respectively. We thank Nuria Melisa Morales-Garcia for extensive data
visualization discussion and designing Figures \ref{fig:proposed-models} and
\ref{fig:best-fit-models}. This research was supported by CIHR project grant 437576,
Natural Sciences and Engineering Research Council of Canada (NSERC) grant RGPIN-2017-04816, 
and the Canada Research Chair program. 
This research was supported by an NIH grant
R35GM133531 (to BMH). The content is solely the responsibility of the authors
and does not necessarily represent the official views of the National
Institutes of Health.

@@

APR, BMH, and SG designed the study.
BMH, EGA, EH, and MM designed and conducted participant recruitment.
APR, BMH, and SG designed statistical analyses.
APR conducted statistical analyses. 
APR, TDW, BMH, and SG interpreted the results and wrote the first draft of the article. 
All authors read and edited the article.

@@

Nama sequencing data are available from the European Genome-Phenome Archive
(EGA), accession number: EGAD00001006198. The African Diversity Reference Panel
can be found at accession: EGAS00001000960.

>>>>

We are grateful for the DNA contribution from each participant that enabled
this study; in particular we wish to highlight the generous participation of
the Richtersveld Nama community in South Africa and help from local research
assistants Willem DeKlerk and Hendrik Kaimann. Additional assistance and
community engagement was conducted by Justin Myrick, Chris Gignoux, Caitlen
Uren and Cedric Werely. We thank the African Genome Diversity Project for data
generation, including Tommy Carensten, Deepti Gurdasani, and Manj Sandhu. We
thank Luke Anderson-Trocm\'e and Georgette Femerling for assistance in creating
the map in Figure~\ref{fig:diversity} and Figure \ref{fig:toymodels},
respectively. We thank Nuria Melisa Morales-Garcia for extensive data
visualization discussion and designing Figures \ref{fig:proposed-models} and
\ref{fig:best-fit-models}. This research was supported by CIHR project grant 437576,
Natural Sciences and Engineering Research Council of Canada (NSERC) grant RGPIN-2017-04816, 
and the Canada Research Chair program to SG. 
This research was supported by an NIH grant
R35GM133531 to BMH. The content is solely the responsibility of the authors
and does not necessarily represent the official views of the National
Institutes of Health. MM and EH acknowledge the support of the DSI-NRF Centre of Excellence for 
Biomedical Tuberculosis Research, South African Medical Research Council Centre for Tuberculosis 
Research, Division of Molecular Biology and Human Genetics, Faculty of Medicine and Health Sciences, 
Stellenbosch University, Cape Town, South Africa.

@@

APR, BMH, and SG designed the study.
BMH, EH, and MM designed and conducted participant recruitment.
BMH and EGA performed quality control of data.
APR, BMH, and SG designed statistical analyses.
APR conducted statistical analyses. 
APR, TDW, BMH, and SG interpreted the results and wrote the first draft of the article. 
All authors read and edited the article.

@@

Nama sequencing data are available from the European Genome-Phenome Archive
(EGA), accession number: EGAD00001006198. Data access is permitted for non-commercial, 
population origins or ancestry research
upon application to the South African Data Access Committee with appropriate IRB approval. 
The African Diversity Reference Panel can be found at accession: EGAS00001000960.
